Random Generation of Rich \\ Abstract Data Type Values

### 2019-01-24 paper/randomtesting.tex
Done for today
Till Section III

\end{code}
%
The type |Html| allows to build pages via four possible constructions:
|Text|---which represents plain text values---, |Single| and |Tag|---which
represent singular and paired Html tags, respectively---, and |Join|---which
concats two Htmls pages one after another.
%
% In the previous definition, we declare |Html| as the sum of four possible
% constructions: |Text| represents plain text values. |Sing| and |Tag| represent
% singular and paired Html tags, and |Join| concats two expression one after
% another.
% %
% We only encode a very small subset of the actual Html specification for
% illustrative reasons.
% %
In Haskell, |Text|, |Single|, |Tag|, and |Join| are known as \emph{data
  constructors} (or constructors for short) and are used to distiguish which
variant of the ADT we are constructing.
%
Each data constructor is defined as a product of zero or more types known as
\emph{fields}.
%
For instance, |Text| has a field of type |String|, whereas |Join| two recusive
fields of type |Html|.
%
In general, we will say that a data constructor with no recursive fields is
\emph{terminal}, and \emph{non-terminal} or \emph{recursive} if it has at least
one field of such nature.
%
With this representation, the page ``|html_example|'' can be encoded as:
%
\begin{code}
Tag "html" (Join (Join
  (Text "hello") (Sing "hr")) (Text "bye"))
\end{code}
%
% Additionally, we can define a function |render| to serialize |Html| values as
% follows:
% %
% \begin{code}
% render :: Html -> String
% render (Text t) = t
% render (Sing t) = "<" ++ t ++ ">"
% render (Join x y) = render x ++ render y
% render (Tag t x)
%   = "<" ++ t ++ ">" ++ render x ++ "</" ++ t ++ ">"
% \end{code}

@@

\subsection*{\textbf{Type-Driven Generation of Random Values}}

>>>>

\end{code}
%
The type |Html| allows to build pages via four possible constructions:
|Text|---which represents plain text values---, |Single| and |Tag|---which
represent singular and paired Html tags, respectively---, and |Join|---which
concats two Htmls pages one after another.
%
% In the previous definition, we declare |Html| as the sum of four possible
% constructions: |Text| represents plain text values. |Sing| and |Tag| represent
% singular and paired Html tags, and |Join| concats two expression one after
% another.
% %
% We only encode a very small subset of the actual Html specification for
% illustrative reasons.
% %
In Haskell, |Text|, |Single|, |Tag|, and |Join| are known as \emph{data
  constructors} (or constructors for short) and are used to distiguish which
variant of the ADT we are constructing.
%
Each data constructor is defined as a product of zero or more types known as
\emph{fields}.
%
For instance, |Text| has a field of type |String|, whereas |Join| two recusive
fields of type |Html|.
%
In general, we will say that a data constructor with no recursive fields is
\emph{terminal}, and \emph{non-terminal} or \emph{recursive} if it has at least
one field of such nature.
%
With this representation, the page \texttt{<html>hello<hr>bye</html>} can be
encoded as:
%
\begin{code}
Tag "html" (Join (Join
  (Text "hello") (Single "hr")) (Text "bye"))
\end{code}
%
% Additionally, we can define a function |render| to serialize |Html| values as
% follows:
% %
% \begin{code}
% render :: Html -> String
% render (Text t) = t
% render (Sing t) = "<" ++ t ++ ">"
% render (Join x y) = render x ++ render y
% render (Tag t x)
%   = "<" ++ t ++ ">" ++ render x ++ "</" ++ t ++ ">"
% \end{code}

@@

\subsection{Type-driven generation of random values}
